LAGOS lake depth

### 2021-08-04 figures/02_depth_model.Rmd
also turn off 02_depth_model_resid chunk for now

```{r 02_depth_model_resid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# residual = observed - predicted
# positive value = underprediction
# negative value = overprediction

>>>>

```{r 02_depth_model_resid, echo=FALSE, message=FALSE, eval=FALSE, warning=FALSE, results='hide'}
# residual = observed - predicted
# positive value = underprediction
# negative value = overprediction
dt <- readRDS("../data/01_depth_model/depth_model.rds")
